---
title: "Report - Statistical Results Table"
author: "Vince Egalla"
date: "12/30/2020"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dependencies

```{r}
library(tidyverse)
library(plyr)
library(dplyr)
library(countrycode)
library(lubridate)
library(ggplot2)
#library(extrafont)
#font_import()
#library(tabulizer)
```

## Load Data
## Findings
\begin{table}[]
\centering
\caption{}
\label{tab:NFI}
\begin{tabular}{|l|c|c|c|}
\hline & \multicolumn{ 1 }{ c }{ (1) } & \multicolumn{ 1 }{ c }{ (2) } & \multicolumn{ 1 }{ c }{ (3) } \\ 
\hline
\hline
USDA Authority          & 11.45$^{***}$ & 3.27$^{**}$  & -0.63$^{**}$            \\
                        & (1.74)        & (1.15)       & (0.19)               \\
                        & $[t = 6.57]$  &$[t = 2.84]$  &$[t = -3.27]$          \\[4.5pt]
Transition Period       &               & 1.43         & 0.02                 \\
                        &               & (0.78)       & (0.18)                \\
                        &               &$[t = 1.86]$  &$[t = 0.14]$          \\[4.5pt]
Import Volume under FDA &               & -0.29        & -0.01             \\
(million kg)            &               & (0.81)       & (0.04)                \\
                        &               &$[t = -0.35]$ &$[t = -0.34]$           \\[4.5pt]
Import Volume under USDA&               & 2.40$^{***}$ & 0.07$^{**}$            \\
(million kg)            &               & (0.27)       & (0.02)                \\
                        &               &$[t = 8.85]$  &$[t = 2.81]$          \\[4.5pt]
Monthly                 &               &              &                       \\
Fixed Effects           &               &              &                       \\
                        &               &              &                       \\[4.5pt]
Country                 &               &              &                       \\
Fixed Effect            &               &              &                       \\
                        &               &              &                       \\[4.5pt]
Constant                & 0.63$^{**}$   & 2.07         & 1.10                \\
                        & (0.19)        & (1.64)       & (1.11)              \\
                        &$[t = 3.31]$   &$[t = 1.26]$  &$[t = 0.99]$            \\[4.5pt]
$N$                     & 262           & 262          & 262                  \\[4.5pt]
$\hat{\sigma}$          & 8.32          & 6.21         & 0.89                   \\[4.5pt]
$Adjusted R^2$          & 0.278         & 0.598        & 0.080                  \\ 
\hline
\multicolumn{4}{l}{\footnotesize{Standard errors in parentheses}}\\
\multicolumn{4}{l}{\footnotesize{$^*$ indicates significance at $p< 0.05 $}}\\
\multicolumn{4}{l}{\footnotesize{$^{**}$ indicates significance at $p< 0.01 $}}\\ 
\multicolumn{4}{l}{\footnotesize{$^{***}$ indicates significance at $p< 0.001 $}}\\ 
\end{tabular}
\end{table}
