---
title: "Report - Statistical Results Table"
author: "Vince Egalla"
date: "12/30/2020"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dependencies

```{r}
library(tidyverse)
library(plyr)
library(dplyr)
library(countrycode)
library(lubridate)
library(ggplot2)
#library(extrafont)
#font_import()
#library(tabulizer)
```

## Load Data
## Findings
\begin{table}[]
\centering
\caption{}
\label{tab:NFI}
\begin{tabular}{|l|c|c|c|}
\hline & \multicolumn{ 1 }{ c }{ (1) } & \multicolumn{ 1 }{ c }{ (2) } & \multicolumn{ 1 }{ c }{ (3) } \\ 
\hline
\hline
USDA Authority          & 11.45$^{***}$ & 2.39$^{**}$  & -0.69$^{**}$            \\
                        & (1.74)        & (0.84)       & (0.17)               \\
                        & $[t = 6.57]$  &$[t = 2.83]$  &$[t = -3.98]$          \\[4.5pt]
Transition Period       &               & 0.40         & -0.14                 \\
                        &               & (0.47)       & (0.18)                \\
                        &               &$[t = 0.86]$  &$[t = -0.74]$          \\[4.5pt]
Import Volume under FDA &               & -0.62        & -0.08$^{*}$             \\
(million kg)            &               & (0.85)       & (0.04)                \\
                        &               &$[t = -0.74]$ &$[t = -2.02]$           \\[4.5pt]
Import Volume in Transition &           & 0.40         & 0.08$^{**}$             \\
(million kg)            &               & (0.23)       & (0.03)                \\
                        &               &$[t = 1.74]$  &$[t = 3.09]$           \\[4.5pt]
Import Volume under USDA&               & 2.63$^{***}$ & 0.10$^{***}$            \\
(million kg)            &               & (0.28)       & (0.03)                \\
                        &               &$[t = 11.06]$ &$[t = 4.80]$          \\[4.5pt]
Vietnam                 &               & 5.65         & 0.60                      \\
                        &               & (8.01)       & (0.38)                      \\
                        &               &$[t = 0.70]$  &$[t = 1.58]$                     \\[4.5pt]
China                   &               & 0.88         & 0.72$^{***}$                      \\
                        &               & (0.58)       & (0.19)                     \\
                        &               &$[t = 1.52]$  &$[t = 3.76]$                        \\[4.5pt]
Thailand                &               & 0.06         & -0.05                       \\
                        &               & (0.52)       & (0.13)                      \\
                        &               &$[t = 0.11]$  &$[t = -0.35]$                       \\[4.5pt]
Monthly                 &               &In Model,     &In Model,                       \\
Fixed Effects           &               &Not Reported  &Not Reported                       \\
                        &               &              &                       \\[4.5pt]
Constant                & 0.63$^{**}$   & 0.80         & 0.15                \\
                        & (0.19)        & (0.61)       & (0.09)              \\
                        &$[t = 3.31]$   &$[t = 1.32]$  &$[t = 1.76]$            \\[4.5pt]
$N$                     & 262           & 262          & 262                  \\[4.5pt]
$\hat{\sigma}$          & 8.32          & 6.02         & 0.87                   \\[4.5pt]
$Adjusted R^2$          & 0.278         & 0.622        & 0.119                  \\ 
\hline
\multicolumn{4}{l}{\footnotesize{Standard errors in parentheses}}\\
\multicolumn{4}{l}{\footnotesize{$^*$ indicates significance at $p< 0.05 $}}\\
\multicolumn{4}{l}{\footnotesize{$^{**}$ indicates significance at $p< 0.01 $}}\\ 
\multicolumn{4}{l}{\footnotesize{$^{***}$ indicates significance at $p< 0.001 $}}\\ 
\end{tabular}
\end{table}
